---
title: "Shiny Application and Reproducible Pitch"
author: "Vyomkesh Jha"
date: "October 11, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Data Predictor :: Analysis Report

A data product using shiny apps embedded within RMarkDown.
Traverse using PageUp and PageDown.

## Overview of the application

- The properties of diamonds can be recoginized using several parameters.
- Carat,Price, Sample-size, color and Depth are some of the common parameters.
- This application enables the user to pick the right parameters for the best Diamond selection.


## Application Links

Click the Below Link for the Application.
https://ultimagic.shinyapps.io/DiamondPred/

Github:
https://github.com/punkstorm28/Shiny
## Data Used
The Diamonds Data Set from ggplot2 package was used which contains information about 53940 diamonds across 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```